InteroceptionScale - Data Analysis

### 2024-11-25 study1/analysis/2_analysis.qmd
Update 2_analysis.qmd

---
title: "InteroceptionScale - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

items <- select(df, contains("_Q")) 
byfacet <- items[df$Condition=="Dimensions",]
bymodality <- items[df$Condition=="Domains",]
byrandom <- items[df$Condition=="Random",]

@@

  Nociception_SkinThermo_Q = "My skin is very sensitive to painful stimulations (e.g., pinching)",

@@

# Make 
```

@@

::: {.panel-tabset}

@@

# p1 <- make_heatmap(items, title="Full Sample")
# p1
```

### By Facet

Also "Dimension" / "Domains" / "Context"

```{r}
# p2 <- make_heatmap(byfacet, title="By Facet")
# p2
```

### By Modality

```{r}
# p3 <- make_heatmap(bymodality, title="By Modality")
# p3
```

### Random Grouping

```{r}
# p4 <- make_heatmap(byrandom, title="Random Grouping")
# p4
```

### Figures

```{r}
#| output: false

# p1 <- make_heatmap(items, interactive=FALSE) |>
#   gridExtra::arrangeGrob(top = 'Full Sample')
# p2 <- make_heatmap(byfacet, interactive=FALSE, title="By Facet") |>
#   gridExtra::arrangeGrob(top = 'By Facet')
# p3 <- make_heatmap(bymodality, interactive=FALSE, title="By Modality") |>
#   gridExtra::arrangeGrob(top = 'By Modality')
# p4 <- make_heatmap(byrandom, interactive=FALSE, title="Random Grouping") |>
#   gridExtra::arrangeGrob(top = 'Random Grouping')
```

# gridExtra::grid.arrange(
#   p1, p2, p3, p4,
#   layout_matrix=rbind(
#     c(1,1,1),
#     c(1,1,1),
#     c(2,3, 4)))
```

:::

@@

```{r}
# bootstrap_similarity <- function(df) {
#   rez <- data.frame()
#   for(i in 1:200) {
#     idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
#     newdata <- df[idx,]
#     items <- select(df, contains("_Q"))
#     byfacet <- items[newdata$Condition=="Dimensions",]
#     bymodality <- items[newdata$Condition=="Domains",]
#     byrandom <- items[newdata$Condition=="Random",]
#     
#     rez <- rbind(
#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
#                                          ncomp1=10, ncomp2=10, plot=FALSE),
#       MatrixCorrelation::allCorrelations(cor(items), cor(bymodality), 
#                                          ncomp1=10, ncomp2=10, plot=FALSE)) |>
#       as.data.frame() |> 
#       mutate(
#         Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
#         Sample = c("Random", "Random", "Full", "Full"),
#         Iteration = i) |> 
#       mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |> 
#       rbind(rez)
#   }
#   rez
# }
# 
# 
# rez <- bootstrap_similarity(df)
# 
# rez |> 
#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
#   filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |> 
#   mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |> 
#   ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
#   ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
#   facet_wrap(~Sample) +
#   scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
#   scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
#   labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
#   theme_minimal()
# 
# rez |> 
#   pivot_longer(-c("Comparison", "Sample", "Iteration")) |> 
#   filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |> 
#   ggplot(aes(x=name, y=value)) +
#   ggdist::stat_eye(aes(fill = after_stat(y < 0))) +
#   facet_wrap(~Sample) +
#   geom_hline(yintercept=0, linetype="dashed") +
#   labs(x="Indices of Correlation Matrix Difference", y="Similarity Difference") +
#   theme_minimal() +
#   scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), guide="none")
```

@@

```{r}
uva <- EGAnet::UVA(items, cut.off = 0.2)
# uva

toremove_table <- rbind(
  data.frame(
  Condition = "Full Sample",
  Remove = uva$keep_remove$remove),
  data.frame(
  Condition = "By Facet",
  Remove = EGAnet::UVA(byfacet, cut.off = 0.2)$keep_remove$remove),
  data.frame(
  Condition = "By Modality",
  Remove = EGAnet::UVA(bymodality, cut.off = 0.2)$keep_remove$remove),
  data.frame(
  Condition = "Random Grouping",
  Remove = EGAnet::UVA(byrandom, cut.off = 0.2)$keep_remove$remove)
) |>
  mutate(n = n(), .by=c("Remove")) |>
  mutate(Condition = fct_relevel(Condition, "Full Sample", "By Facet", "By Modality", "Random Grouping")) |>
  arrange(desc(n), Remove, Condition)

toremove <- filter(toremove_table, Condition=="Full Sample" & n > 1)$Remove

toremove_table |>
  select(-n) |>
  gt::gt() |>
  gt::data_color(columns=Remove, fn=\(x) ifelse(x %in% toremove, "#FFEBEE", "white"))
```

```{r}
items <- select(items, -all_of(toremove))
byfacet <- select(byfacet, -all_of(toremove))
bymodality <- select(bymodality, -all_of(toremove))
byrandom <- select(byrandom, -all_of(toremove))
```

@@

ega1 <- bootEGA(
  items,
  EGA.type = "EGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
load("models/ega1.RData")

@@

itemstability_table <- make_loadingtable(itemstability$item.stability$all.dimensions)

toremove2 <- filter(itemstability_table, Max < 0.7)$Item

itemstability_table |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  )
```

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
load("models/ega2.RData")

lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)

@@

lower |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  )
```

@@

lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) 
higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std)) |> 
  select(names(lower)) |> 
  arrange(Item)
higher$Item <- paste0("H", higher$Item)

rbind(higher, lower) |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::tab_row_group(
    label = "Item",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Higher Order",
    rows = 1:nrow(higher)
  ) |> 
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  )
```

@@

tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
  ggraph::ggraph(layout = 'graphopt') +
  ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.1, strength=0) +
  ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
  ggraph::geom_node_text(aes(label=name), repel=TRUE) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
  theme_void()
```

@@

<!-- ```{r} -->
<!-- EGAnet::EGM(items[, 1:60]) -->

@@

<!-- rez <- EGAnet::network.compare(byfacet[, 1:20], bymodality[, 1:20], seed=3) -->
<!-- plot(rez) -->
<!-- ``` -->

### Empirical vs. Model Scores

```{r}
EGAnet::net.scores()
```

>>>>

---
title: "InteroceptionScale - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

items <- select(df, contains("_Q")) 
byfacet <- items[df$Condition=="Dimensions",]
bymodality <- items[df$Condition=="Domains",]
byrandom <- items[df$Condition=="Random",]
```

```{r}

@@

  Nociception_SkinThermo_Q1 = "My skin is very sensitive to painful stimulations (e.g., pinching)",

@@

```

@@

@@

make_heatmap(items, title="Full Sample")
```

@@

```{r}
bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:200) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

    rez <- rbind(
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
      as.data.frame() |>
      mutate(
        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
        Sample = c("Random", "Random", "Full", "Full"),
        Iteration = i) |>
      mutate(d_PSI = diff(PSI), d_RV = diff(RV), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
      rbind(rez)
  }
  rez
}

rez <- bootstrap_similarity(df)

rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(name %in% c("PSI", "RV", "RVadj", "SMI")) |>
  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
  facet_wrap(~Sample) +
  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
  theme_minimal()
```

```{r}
#| fig-width: 10
#| fig-height: 10

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |> 
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="To which matrix is the random one more similar?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#F44336", "FALSE"="#2196F3"), labels = c("By modality", "By facet"))

r <- correlation::cor_sort(cor(byrandom))
order <- colnames(r)

make_corplot <- function(data, order) {
  rownames_to_column(as.data.frame(cor(data)), "item") |> 
    pivot_longer(-item) |> 
    mutate(item = fct_relevel(item, order),
           name = fct_relevel(name, order)) |>
    ggplot(aes(x=name, y=item, fill=value)) +
    geom_tile() +
    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          legend.position = "none")
}

p1 <- make_corplot(byrandom, order) +
  ggtitle("Grouped randomly")
p2 <- make_corplot(byfacet, order) +
  ggtitle("Grouped by facet")
p3 <- make_corplot(bymodality, order) +
  ggtitle("Grouped by modality")

p1 / (p2 | p_sim | p3) + patchwork::plot_layout(heights=c(3, 1)) + patchwork::plot_annotation(title="Effect of Item-presentation Grouping", theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
```

@@

```{r}
#| fig-width: 10
#| fig-height: 8

uva <- EGAnet::UVA(items, cut.off = 0.2)

correlation::correlation(items[unlist(uva$redundant)],
                         items[names(uva$redundant)]) |>
  mutate(Parameter1 = fct_relevel(Parameter1, unlist(uva$redundant)),
         Parameter2 = fct_relevel(Parameter2, names(uva$redundant))) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=insight::format_value(r)), color="white") +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x="Removed Items", y="Kept Items", fill="Correlation")

toremove1 <- uva$keep_remove$remove
```

```{r}
items <- select(items, -all_of(toremove1))
byfacet <- select(byfacet, -all_of(toremove1))
bymodality <- select(bymodality, -all_of(toremove1))
byrandom <- select(byrandom, -all_of(toremove1))
```

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
#| fig-width: 10
#| fig-height: 12

load("models/ega1.RData")

@@

itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)

toremove2 <- filter(itemstability_table, Max < 0.8)$Item

itemstability_table |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "louvain",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

```{r}
#| fig-width: 10
#| fig-height: 12

load("models/ega2.RData")

plot(itemStability(ega2, IS.plot=FALSE))
```

```{r}
lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)

@@

lower |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

@@

higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order)$std))
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega3$EGA$lower_order)$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))

higher$Item <- paste0("H", higher$Item)
higher$Label <- paste("TODO", 1:nrow(higher))
lower <- mutate(lower, Label = labels[Item], Item = 1:n())

rbind(higher, lower) |>
  datawizard::data_relocate("Label", after = "Item") |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::tab_row_group(
    label = "Item",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Higher Order",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label")
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Item"),
      gt::cells_row_groups(groups = "Higher Order")
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCDD2"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(1, 6:8))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCCBC"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(9:11))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFE0B2"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(12:14))
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  )
```

```{r}
# REMOVE ONCE https://github.com/hfgolino/EGAnet/pull/167 is merged
convert2tidygraph <- function(EGA.object)
{

  if("bootEGA" %in% class(EGA.object)) {
    # Bootstrapped EGA ---
    if(!"typicalGraph" %in% names(EGA.object)) {
      stop("The bootEGA object must contain a typicalGraph object. Set `typicalStructure=TRUE`.")
    }

    if("lower_order" %in% names(EGA.object$typicalGraph)) {
      # Hierarchical EGA ---
      lower_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$lower_order$wc)
      lower_nodes$dimension <- paste0("L", lower_nodes$dimension)  # Discriminate from higher
      lower_nodes$level <- "Lower"
      higher_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$higher_order$wc)
      higher_nodes$name <- paste0("L", as.numeric(higher_nodes$name))
      higher_nodes$dimension <- paste0("H", higher_nodes$dimension)  # Discriminate from lower
      higher_nodes$level <- "Higher"
      nodes <- rbind(lower_nodes, higher_nodes)

      lower_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$lower_order$graph)
      higher_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$higher_order$graph)
      higher_edges$from <- paste0("L", as.numeric(higher_edges$from))
      higher_edges$to <- paste0("L", as.numeric(higher_edges$to))
      edges <- rbind(lower_edges, higher_edges)
      edges$type <- "real"

      # Make edges from lower to higher order
      for(i in 1:nrow(lower_nodes)) {
        edges <- rbind(
          edges,
          data.frame(from = lower_nodes$name[i], to = lower_nodes$dimension[i], link = 1, type = "virtual")
          )
      }
    } else {
      # Non-hierarchical EGA ---
      nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$wc)
      edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$graph)
    }

  } else {
    # Normal EGA ---
    nodes <- .convert2tidygraph_nodes(EGA.object$wc)
    edges <- .convert2tidygraph_edges(EGA.object$network)
  }

  # Return result
  return(
    list(
      nodes = nodes,
      edges = edges[edges$link != 0,]
    )
  )
}

#' @keywords internal
#' @noRd
.convert2tidygraph_nodes <- function(wc){
  data.frame(
    name = names(wc),
    dimension = as.character(wc)
  )
}

#' @keywords internal
#' @noRd
.convert2tidygraph_edges <- function(network){
  data.frame(
    from = rep(rownames(network), times = ncol(network)),
    to = rep(colnames(network), each = nrow(network)),
    link = as.vector(network)
  )
}
```

@@

tidygraph::tbl_graph(graph$nodes, edges=graph$edges, directed=FALSE) |>
  ggraph::ggraph(layout = 'mds') +
  ggraph::geom_edge_arc(aes(edge_alpha=as.numeric(type == "virtual")), edge_width=0.2, strength=0, color="grey") +
  ggraph::geom_edge_arc(aes(edge_color = link, edge_width = abs(link), edge_alpha=as.numeric(type == "real")), strength=0.1) +
  ggraph::geom_node_point(aes(color=dimension, shape=level), size=10, alpha=0.7) +
  ggraph::geom_node_text(aes(label=name), repel=TRUE) +
  scale_edge_alpha(range = c(0, 0.9), guide="none") +
  scale_edge_width(range = c(0.2, 3), guide="none") +
  scale_shape_manual(values=c("Higher"="square", "Lower"="circle")) +
  theme_void()
```

@@

<!-- ```{r} -->
<!-- # EGAnet::EGM(items[, 1:60]) -->

@@

<!-- # rez <- EGAnet::network.compare(byfacet, bymodality, seed=3) -->
<!-- # plot(rez) -->
<!-- ``` -->

## Empirical vs. Model Scores

```{r}
# Modelbased scores
scores <- EGAnet::net.scores(
  items[names(ega3$typicalGraph$lower_order$wc)],
  A=ega3$typicalGraph$lower_order$graph,
  wc=ega3$typicalGraph$lower_order$wc)$scores$std.scores |>
  as.data.frame()
names(scores) <- paste0("C", names(scores))

# Empirical scores
clusters <- data.frame(Item = names(ega3$typicalGraph$lower_order$wc),
                       Cluster = ega3$typicalGraph$lower_order$wc) |>
  mutate(Cluster = paste0("E", sprintf("%02d", Cluster)))

empirical <- data.frame(Participant=df$Participant)
for(c in unique(clusters$Cluster)) {
  s <- rowMeans(items[clusters[clusters$Cluster==c, "Item"]])
  empirical <- cbind(empirical, setNames(data.frame(x = s), c))
}

correlation::correlation(empirical, scores) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=sprintf("%.2f", r)), size=3) +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
  labs(x="Empirical Scores", y="Model Scores") +
  theme_minimal()
```
